PLAE enables quick and easy searching across one million ocular transcriptomes

### 2022-07-19 manuscript_00.Rmd
tweak diff heatmap

```{r}
# tic()
# ws_oct <- ws_table %>% filter(`Well Supported` == 'Yes') %>% pull(`CellType (Predict)`)
# 
consist_diff2 <- scEiaD_2020_v01 %>%
  tbl("diff_testing") %>%
  filter(Base %in% ws_oct) %>%
  filter(Group == 'CellType (Predict)',
         Against == 'All',
         Organism %in% c('Homo sapiens','Mus musculus')) %>%
  group_by(Base, Gene) %>%
  summarise(`mean log2FC` = mean(log2FoldChange), `sig count` = sum(padj < 1e-5), `mean padj` = mean(padj)) %>%
  filter(`mean log2FC` > 2, `sig count` > 1, `mean padj` < 1e-5) %>%
  collect() %>%
  mutate(GENEID = str_extract(Gene, 'ENS\\w+')) %>%
  left_join(gene_tab, by = 'GENEID') %>%
  relocate(SYMBOL, GENEID) %>%
  dplyr::rename(Symbol = SYMBOL, ID = GENEID) %>%
  arrange(-`mean log2FC`)

@@

diff_tab_sup %>% flextable()
```

@@

ws_table %>% flextable()
```

@@

meta_filter %>% group_by(Citation, PMID, organism, study_accession) %>% summarise(Count = n(), Tissues = paste(unique(Tissue), collapse = ', ')) %>% flextable()
```

>>>>

```{r}
# tic()
# ws_oct <- ws_table %>% filter(`Well Supported` == 'Yes') %>% pull(`CellType (Predict)`)
# 
# consist_diff <- scEiaD_2020_v01 %>%
#   tbl("diff_testing") %>%
#   filter(Base %in% ws_oct) %>%
#   filter(Group == 'CellType (Predict)',
#          Against == 'All',
#          Organism %in% c('Homo sapiens','Mus musculus')) %>%
#   group_by(Base, Gene) %>%
#   summarise(`mean log2FC` = mean(log2FoldChange), `sig count` = sum(padj < 1e-5), `mean padj` = mean(padj)) %>%
#   filter(`mean log2FC` > 2.463, `sig count` > 1, `mean padj` < 1e-5) %>%
#   collect() %>%
#   mutate(GENEID = str_extract(Gene, 'ENS\\w+')) %>%
#   left_join(gene_tab, by = 'GENEID') %>%
#   relocate(SYMBOL, GENEID) %>%
#   dplyr::rename(Symbol = SYMBOL, ID = GENEID) %>%
#   arrange(-`mean log2FC`)

@@

diff_tab_sup %>% flextable() %>% autofit() %>% fit_to_width(7)
```

@@

ws_table %>% flextable() %>% autofit() %>% fit_to_width(7)
```

@@

meta_filter %>% group_by(Citation, PMID, organism, study_accession) %>% summarise(Count = n(), Tissues = paste(unique(Tissue), collapse = ', ')) %>% flextable() %>% autofit() %>% fit_to_width(7)
```
